Addition and removal energies of circular quantum dots

### 2017-06-13 Manuscript/paper.tex
bibtex and paper.tex update

The ground states of quantum dots exhibit shell structures and magic numbers similar to those of atoms and nuclei \cite{tarucha1996}.  Thus, they provide a rare opportunity to study electronic systems without the influence of the atomic nuclei.  They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops \cite{bogner2010}.

@@

The SRG flow equation Eq.\ \eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.  However, since the basis of a many-body problem grows factorially with the number of particles and the size of the model space, the applicability of the naive (free-space) SRG method is restricted to comparatively small systems.  A more practical approach is to perform the evolution \textit{in medium}, i.e.\ using a many-body Slater determinant as a reference \cite{kehrein2006flow}.  This gives rise to the IM-SRG method \cite{bogner2012,Hergert2016165,lnp936}.

>>>>

The ground states of quantum dots exhibit shell structures and magic numbers similar to those of atoms and nuclei \cite{tarucha1996}.  Thus, they provide a rare opportunity to study electronic systems without the influence of the atomic nuclei.  They also provide a testbed for the development of many-body methods for other systems with similar geometry, such as nuclei or neutrons drops \cite{PhysRevC.84.044306}.

@@

The SRG flow equation Eq.\ \eqref{eq:imsrgode} can be solved in the second quantization formalism described in Section \ref{subsec:modelHamiltonian}, where field operators are defined with respect to the physical vacuum state.  However, since the basis of a many-body problem grows factorially with the number of particles and the size of the model space, the applicability of the naive (free-space) SRG method is restricted to comparatively small systems.  A more practical approach is to perform the evolution \textit{in medium}, i.e.\ using a many-body Slater determinant as a reference \cite{kehrein2006flow}.  This gives rise to the IM-SRG method \cite{PhysRevC.85.061304,Hergert2016165,lnp936}.
